Parsing Postfix Log Files

### 2009-08-24 doc/logparser-complications.tex
Changes made to improve appearance after switching to one-and-a-half spacing.
Changes to capitalisation of titles, as specified by Howard Hamilton. Fixed that/than type identified by Joe Carthy.

\section{Complications Encountered While Writing The \parsernamelong{}}

@@

\texttt{3FF7C4317: to=<username@example.com>, relay=local, \hfill{}
\newline{} \tab{} \tab{} delay=0, status=sent (forwarded as 56F5B43FD)}

@@

\subsection{Out Of Order Log Lines}

@@

\subsection{Mail Deleted Before Delivery Is Attempted}

@@

\subsection[Bounce Notification Mails Delivered Before Their Creation Is
Logged]{Bounce Notification Mails Delivered Before \newline{} Their
Creation Is Logged}

@@

\subsection{Mails Deleted During Delivery}

>>>>

\section{Complications Encountered During Development of the \parsernamelong{}}

@@

\texttt{\tab{} 3FF7C4317: to=<username@example.com>, relay=local, \hfill{}
\newline{} \tab{} \tab{} \tab{} delay=0, status=sent (forwarded as
56F5B43FD)}

@@

\subsection{Out of Order Log Lines}

@@

\subsection{Mail Deleted Before Delivery is Attempted}

@@

\subsection[Bounce Notification Mails Delivered Before their Creation is
Logged]{Bounce Notification Mails Delivered Before \newline{} their
Creation Is Logged}

@@

\subsection{Mails Deleted from the Mail Queue During Delivery}

### 2009-08-24 doc/logparser-results.tex
Changes to capitalisation of titles, as specified by Howard Hamilton. Fixed that/than type identified by Joe Carthy.

\subsection{Characteristics Of The \numberOFlogFILES{} Log Files}

@@

\subsection{Rule Ordering For Efficiency}

@@

\subsection{Comparing Optimal Ordering Against An Oracle}

@@

\subsection{Scalability As The Ruleset Grows}

@@

\subsection{Where Is Parsing Time Spent: Recognising Or Processing Log
Lines?}

@@

\subsection{Mail Delivery Attempts Correctly Understood And Reconstructed}

>>>>

\subsection{Characteristics of the \numberOFlogFILES{} Log Files}

@@

\subsection{Rule Ordering for Efficiency}

@@

\subsection{Comparing Optimal Ordering Against an Oracle}

@@

\subsection{Scalability as the Ruleset Grows}

@@

\subsection{Where is Parsing Time Spent: Recognising or Processing Log
Lines?}

@@

\subsection{Mail Delivery Attempts Correctly Understood and Reconstructed}
